### 2013-12-11 article2013.Rmd
Commented on the country grouping part of the article
more commenting
another row added
Esimerkkiviesti Anulle
Tähän saakka tehtyä:
- koska gini-muuttujassa oli vähän ongelmia (1. tiedot vähän miltä vuosilta sattuu, 2. EI TILASTOLLISESTI MERKITSEVÄ, 3. teoreettisesti hieman epävarma) niin kokeilin laskea koetun eriarvoisuuden ginin aineistosta. Se on nyt mukana niin paperin kuvioissa kun myös ainakin osassa regressioita.
- Maaryhmittely on vielä mukana teksteissä, mutta sen voisi jättää kokonaan pois. Sitä ei ole analyyseissä ollutkaan hetkeen, mutta sen voisi jättää pois teoriasta, abstraktis

% Attributions for Poverty in Post-Socialist Countries[^*]
% Markus Kainu[^**];Mikko Niemelä[^***]
% November 19, 2013

[^*]:*Work in progress. See the computation analysis at [research.muuankarski.org/attributions/](http://research.muuankarski.org/attributions/)

@@

From the perspective of value structure, the role of "socialist or soviet legacy" in poverty attributions is worth of considering. Murthi and Tiongson (2008) reviewed large body of literature on East-West differences in preferences for redistribution of which vast majority supported the "socialist legacy". By socialist legacy they meant that "owing to the legacy of the past there is a strong preference for income equality and redistributive state spending in post-socialist countries". While testing the findings of previous studies on East-West differences, this study explores the effect of country groups with different socialist and post-socialist past. In order to explore the differences between market economies and post-socialist countries, but also within the "ex-soviet bloc", the study divides post-socialist countries into two groups: Central Eastern Europe (CEE) and Commonwealth of Independent States (CIS) countries. In order to examine the distinctiveness of post-socialist perceptions descriptive analyses include also a selection of Western European countries.

@@

@@

There is also a substantial variation in the level of income inequality among post-socialist countries. Figure 3 shows that the higher level of income inequality is associated with higher level of social blame. As for individual blame type of explanation the picture is more puzzled, showing only weak connection between larger inequality and lower support for individual blame explanation. Again, the Western European countries differ with post-socialist countries. Cross-national differences in income inequality are much smaller in Western Europe than among post-socialist countries. There is a weak negative association between the social blame and income  inequality and a strong positive association between the individual blame and income inequality.

@@

Table 4 and 5 present figures for multilevel logistic analysis. Calculating R² or residual standard deviation makes no sense in the case of logistic regression or other binomial models. Instead, we use \emph{deviance} as our primary statistical summary of logistic model fit. Deviance can be treated as similar to residual standard deviation for generalized linear models. Basically, deviance is a measure of error, and lower deviance implicates better fit to data. When a random predictor is added to model, we expect deviance to decrease, on average, by 1. When predictor is more informative deviance should decrease more than 1. (Gelman and Hill, 2007). As for getting sensible interpretation of the regression coefficients in logistic regression we can divide the coefficients by 4 to get the probability of certain covariate.

@@

Table 4 and 5 present figures for multilevel logistic analysis. Calculating R² or residual standard deviation makes no sense in the case of logistic regression or other binomial models. Instead, we use \emph{deviance} as our primary statistical summary of logistic model fit. Deviance can be treated as similar to residual standard deviation for generalized linear models. Basically, deviance is a measure of error, and lower deviance implicates better fit to data. When a random predictor is added to model, we expect deviance to decrease, on average, by 1. When predictor is more informative deviance should decrease more than 1. (Gelman and Hill, 2007). As for getting sensible interpretation of the regression coefficients in logistic regression we can divide the coefficients by 4 to get the probability of certain covariate.

>>>>

% Attributions for Poverty in Post-Socialist Countries[^*]
% Markus Kainu[^**];Mikko Niemelä[^***]
% December 11, 2013

[^*]:*Work in progress. See the analysis outputs at [http://muuankarski.github.io/attributions/](http://muuankarski.github.io/attributions/)

@@

>From the perspective of value structure, the role of "socialist or soviet legacy" in poverty attributions is worth of considering. Murthi and Tiongson (2008) reviewed large body of literature on East-West differences in preferences for redistribution of which vast majority supported the "socialist legacy". By socialist legacy they meant that "owing to the legacy of the past there is a strong preference for income equality and redistributive state spending in post-socialist countries". While testing the findings of previous studies on East-West differences, this study explores the effect of country groups with different socialist and post-socialist past. In order to explore the differences between market economies and post-socialist countries, but also within the "ex-soviet bloc", the study divides post-socialist countries into two groups: Central Eastern Europe (CEE) and Commonwealth of Independent States (CIS) countries. In order to examine the distinctiveness of post-socialist perceptions descriptive analyses include also a selection of Western European countries.

@@

<!--

@@

-->

![**Perceived inequality from data** and support for social (top) and individual (bottom) blame types of attributions for poverty](figure/scatter_perGini.pdf)

>There is also a substantial variation in the level of income inequality among post-socialist countries. Figure 3 shows that the higher level of income inequality is associated with higher level of social blame. As for individual blame type of explanation the picture is more puzzled, showing only weak connection between larger inequality and lower support for individual blame explanation. Again, the Western European countries differ with post-socialist countries. Cross-national differences in income inequality are much smaller in Western Europe than among post-socialist countries. There is a weak negative association between the social blame and income  inequality and a strong positive association between the individual blame and income inequality.

@@

@@

Table 4 and 5 present figures for multilevel logistic analysis. Calculating R squared or residual standard deviation makes no sense in the case of logistic regression or other binomial models. Instead, we use \emph{deviance} as our primary statistical summary of logistic model fit. Deviance can be treated as similar to residual standard deviation for generalized linear models. Basically, deviance is a measure of error, and lower deviance implicates better fit to data. When a random predictor is added to model, we expect deviance to decrease, on average, by 1. When predictor is more informative deviance should decrease more than 1. (Gelman and Hill, 2007). As for getting sensible interpretation of the regression coefficients in logistic regression we can divide the coefficients by 4 to get the probability of certain covariate.

### 2013-12-11 finalPlots.Rmd
Changed the toc font size in css
Some Sunday evening edits..
Tähän saakka tehtyä:
- koska gini-muuttujassa oli vähän ongelmia (1. tiedot vähän miltä vuosilta sattuu, 2. EI TILASTOLLISESTI MERKITSEVÄ, 3. teoreettisesti hieman epävarma) niin kokeilin laskea koetun eriarvoisuuden ginin aineistosta. Se on nyt mukana niin paperin kuvioissa kun myös ainakin osassa regressioita.
- Maaryhmittely on vielä mukana teksteissä, mutta sen voisi jättää kokonaan pois. Sitä ei ole analyyseissä ollutkaan hetkeen, mutta sen voisi jättää pois teoriasta, abstraktista ja todeta jotain siitä, miksi emme alaryhmittel

```{r, eval=FALSE, echo=FALSE}
setwd("~/workspace/lits/attributions/")
library(knitr)
library(markdown)
knit2html('finalPlots.Rmd', 
          stylesheet="~/workspace/web/css/rmarkdown.css",
          options = c('toc', markdown::markdownHTMLOptions(TRUE)))
```

@@

# valitaan vaan kohdemaat #
t3 <- subset(macro, group_fine != 'West Europe')
west <- subset(macro, group_fine == 'West Europe')
#t3 <- macro
#########################################
t3$group1 <- "group1"
func <- function(t3)
{
  return(data.frame(COR = cor(t3$socialBlame, t3$gdpchange07.10)))
}
df.cor <- ddply(t3, .(group1), func)
t4 <- join(t3,df.cor,by="group1")
cnames <- round(stats:::aggregate.formula(cbind(socialBlame, gdpchange07.10) ~ COR, data=t4, mean),2)

plot1 <- ggplot(t4, aes(x=gdpchange07.10, y=socialBlame, 
                        label=cntry)) +
  geom_smooth(method=lm, se=FALSE,  alpha=.5, linetype="dashed", size=0.5) +  
  geom_text(data=cnames, aes(gdpchange07.10,socialBlame, label = COR, group=COR), 
            size=2.5, color="black") +
  geom_text(size=2, vjust=-0.8, hjust=0.5) +
  geom_point(size=1.5) +
  geom_point(data=t4, aes(x=gdpchange07.10, 
                          y=socialBlame, color=group_general)) +
  # west reference
  geom_point(data=west, aes(x=gdpchange07.10, 
                          y=socialBlame, 
                            color=group_general), alpha=.5) +
  geom_text(data=west, aes(x=gdpchange07.10, 
                           y=socialBlame, label=cntry),
             alpha=.5, size=2, vjust=-0.8, hjust=0.5) +
  # west reference
  labs(x = "Change in GDP between 2007 and 2010 (%)", 
       y = "Support for social blame type of explanation (%)") + 
  scale_colour_manual(values=cbPalette) +
  coord_cartesian(xlim=c(-25,100)) +
  theme_minimal() +
  theme(legend.title=element_blank()) +
  theme(legend.text=element_text(size=6)) +
  theme(legend.position="top") +
  theme(axis.title.y = element_text(size=6)) +
  theme(axis.title.x = element_text(size=6)) +
  theme(axis.text.y = element_text(size=6)) +
  theme(axis.text.x = element_text(size=6)) +
  #guides(color = guide_legend(nrow = 2)) +
  theme(legend.key.size = unit(3, "mm"))

func <- function(t3)
{
  return(data.frame(COR = cor(t3$individualBlame, t3$gdpchange07.10)))
}
df.cor <- ddply(t3, .(group1), func)
t4 <- join(t3,df.cor,by="group1")
cnames <- round(stats:::aggregate.formula(cbind(individualBlame, gdpchange07.10) ~ COR, data=t4, mean),2)
plot2 <- ggplot(t4, aes(x=gdpchange07.10, 
                        y=individualBlame, label=cntry)) +
  geom_smooth(method=lm, se=FALSE,  alpha=.5, linetype="dashed", size=0.5) +  
  geom_text(size=2, vjust=-0.8, hjust=0.5, color="black") +
  geom_text(data=cnames, aes(gdpchange07.10,individualBlame, label = COR, group=COR), 
            size=2.5, color="black") +
  geom_point(size=1.5) +
  geom_point(data=t4, aes(x=gdpchange07.10, 
             y=individualBlame, color=group_general)) +
  # west reference
  geom_point(data=west, aes(x=gdpchange07.10, 
                            y=individualBlame, 
                            color=group_general), alpha=.5) +
  geom_text(data=west, aes(x=gdpchange07.10, 
                           y=individualBlame, label=cntry),
             alpha=.5, size=2, vjust=-0.8, hjust=0.5) +
  # west reference
  labs(x = "Change in GDP between 2007 and 2010 (%)", 
       y = "Support for individual blame type of explanation (%)") +
  scale_colour_manual(values=cbPalette) +
  coord_cartesian(xlim=c(-25,100)) +
  theme_minimal() +
  theme(legend.title=element_blank()) +
  theme(legend.text=element_text(size=6)) +
  theme(legend.position="top") +
  theme(axis.title.y = element_text(size=6)) +
  theme(axis.title.x = element_text(size=6)) +
  theme(axis.text.y = element_text(size=6)) +
  theme(axis.text.x = element_text(size=6)) +
  #guides(color = guide_legend(nrow = 2)) +
  theme(legend.key.size = unit(3, "mm"))

@@

func <- function(t3)
{
  return(data.frame(COR = cor(t3$socialBlame, t3$perGini)))
}
df.cor <- ddply(t3, .(group1), func)
t4 <- join(t3,df.cor,by="group1")
cnames <- round(stats:::aggregate.formula(cbind(socialBlame, perGini) ~ COR, data=t4, mean),2)
plot1 <- ggplot(t4, aes(x=perGini, y=socialBlame, 
                        label=cntry)) +
  geom_smooth(method=lm, se=FALSE,  alpha=.5, linetype="dashed", size=0.5) +
  geom_text(size=2, vjust=-0.8, hjust=0.5) +
  geom_text(data=cnames, aes(perGini,socialBlame, label = COR, group=COR), 
            size=2.5, color="black") +
  labs(x = "Perceived inequality from data", 
       y = "Support for social blame type of explanation (%)") +
  geom_point(size=1.5) +
  geom_point(data=t4, aes(x=perGini, 
                          y=socialBlame, color=group_general)) +
  # west reference
  geom_point(data=west, aes(x=perGini, 
                            y=socialBlame, 
                            color=group_general), alpha=.5) +
  geom_text(data=west, aes(x=perGini, 
                           y=socialBlame, label=cntry),
             alpha=.5, size=2, vjust=-0.8, hjust=0.5) +
  # west reference
  scale_colour_manual(values=cbPalette) +
  #coord_cartesian(xlim=c(-2,2)) +
  theme_minimal() +
  theme(legend.title=element_blank()) +
  theme(legend.text=element_text(size=6)) +
  theme(legend.position="top") +
  theme(axis.title.y = element_text(size=6)) +
  theme(axis.title.x = element_text(size=6)) +
  theme(axis.text.y = element_text(size=6)) +
  theme(axis.text.x = element_text(size=6)) +
  #guides(color = guide_legend(nrow = 2)) +
  theme(legend.key.size = unit(3, "mm"))

func <- function(t3)
{
  return(data.frame(COR = cor(t3$individualBlame, t3$perGini)))
}
df.cor <- ddply(t3, .(group1), func)
t4 <- join(t3,df.cor,by="group1")
cnames <- round(stats:::aggregate.formula(cbind(individualBlame, perGini) ~ COR, data=t4, mean),2)
plot2 <- ggplot(t4, aes(x=perGini, 
                        y=individualBlame, label=cntry)) +
geom_smooth(method=lm, se=FALSE,  alpha=.5, linetype="dashed", size=0.5) +
  geom_text(size=2, vjust=-0.8, hjust=0.5) +
  geom_text(data=cnames, aes(perGini,individualBlame, label = COR, group=COR), 
            size=2.5, color="black") +
  labs(x ="Perceived inequality from data", 
       y = "Support for individual blame type of explanation (%)") +
  geom_point(size=1.5) +
  geom_point(data=t4, aes(x=perGini, 
                          y=individualBlame, color=group_general)) +
  # west reference
  geom_point(data=west, aes(x=perGini, 
                            y=individualBlame, 
                            color=group_general), alpha=.5) +
  geom_text(data=west, aes(x=perGini, 
                           y=individualBlame, label=cntry),
             alpha=.5, size=2, vjust=-0.8, hjust=0.5) +
  # west reference
  scale_colour_manual(values=cbPalette) +
  #coord_cartesian(xlim=c(-2,2)) +
  theme_minimal() +
  theme(legend.title=element_blank()) +
  theme(legend.text=element_text(size=6)) +
  theme(legend.position="top") +
  theme(axis.title.y = element_text(size=6)) +
  theme(axis.title.x = element_text(size=6)) +
  theme(axis.text.y = element_text(size=6)) +
  theme(axis.text.x = element_text(size=6)) +
  #guides(color = guide_legend(nrow = 2)) +
  theme(legend.key.size = unit(3, "mm"))

@@

library(RColorBrewer)
library(mapproj)
library(maptools)
library(rgdal)
map <- suppressWarnings(readOGR(dsn="/home/aurelius/workspace/data/shapefiles/lits/", 
                                layer="lits_all_simple"))

>>>>

@@

# valitaan vaan kohdemaat #
t3 <- subset(macro, group_fine != 'West Europe')
west <- subset(macro, group_fine == 'West Europe')
#t3 <- macro
#########################################
t3$group1 <- "group1"
func <- function(t3)
{
  return(data.frame(COR = cor(t3$socialBlame, t3$gdpChange)))
}
df.cor <- ddply(t3, .(group1), func)
t4 <- join(t3,df.cor,by="group1")
cnames <- round(stats:::aggregate.formula(cbind(socialBlame, gdpChange) ~ COR, data=t4, mean),2)

plot1 <- ggplot(t4, aes(x=gdpChange, y=socialBlame, 
                        label=cntry)) +
  geom_smooth(method=lm, se=FALSE,  alpha=.5, linetype="dashed", size=0.5) +  
  geom_text(data=cnames, aes(gdpChange,socialBlame, label = COR, group=COR), 
            size=2.5, color="black") +
  geom_text(size=2, vjust=-0.8, hjust=0.5) +
  geom_point(size=1.5) +
  geom_point(data=t4, aes(x=gdpChange, 
                          y=socialBlame, color=group_general)) +
  # west reference
  geom_point(data=west, aes(x=gdpChange, 
                          y=socialBlame, 
                            color=group_general), alpha=.5) +
  geom_text(data=west, aes(x=gdpChange, 
                           y=socialBlame, label=cntry),
             alpha=.5, size=2, vjust=-0.8, hjust=0.5) +
  # west reference
  labs(x = "Change in GDP between 2007 and 2010 (%)", 
       y = "Support for social blame type of explanation (%)") + 
  scale_colour_manual(values=cbPalette) +
  coord_cartesian(xlim=c(-25,100)) +
  theme_minimal() +
  theme(legend.title=element_blank()) +
  theme(legend.text=element_text(size=6)) +
  theme(legend.position="top") +
  theme(axis.title.y = element_text(size=6)) +
  theme(axis.title.x = element_text(size=6)) +
  theme(axis.text.y = element_text(size=6)) +
  theme(axis.text.x = element_text(size=6)) +
  #guides(color = guide_legend(nrow = 2)) +
  theme(legend.key.size = unit(3, "mm"))

func <- function(t3)
{
  return(data.frame(COR = cor(t3$individualBlame, t3$gdpChange)))
}
df.cor <- ddply(t3, .(group1), func)
t4 <- join(t3,df.cor,by="group1")
cnames <- round(stats:::aggregate.formula(cbind(individualBlame, gdpChange) ~ COR, data=t4, mean),2)
plot2 <- ggplot(t4, aes(x=gdpChange, 
                        y=individualBlame, label=cntry)) +
  geom_smooth(method=lm, se=FALSE,  alpha=.5, linetype="dashed", size=0.5) +  
  geom_text(size=2, vjust=-0.8, hjust=0.5, color="black") +
  geom_text(data=cnames, aes(gdpChange,individualBlame, label = COR, group=COR), 
            size=2.5, color="black") +
  geom_point(size=1.5) +
  geom_point(data=t4, aes(x=gdpChange, 
             y=individualBlame, color=group_general)) +
  # west reference
  geom_point(data=west, aes(x=gdpChange, 
                            y=individualBlame, 
                            color=group_general), alpha=.5) +
  geom_text(data=west, aes(x=gdpChange, 
                           y=individualBlame, label=cntry),
             alpha=.5, size=2, vjust=-0.8, hjust=0.5) +
  # west reference
  labs(x = "Change in GDP between 2007 and 2010 (%)", 
       y = "Support for individual blame type of explanation (%)") +
  scale_colour_manual(values=cbPalette) +
  coord_cartesian(xlim=c(-25,100)) +
  theme_minimal() +
  theme(legend.title=element_blank()) +
  theme(legend.text=element_text(size=6)) +
  theme(legend.position="top") +
  theme(axis.title.y = element_text(size=6)) +
  theme(axis.title.x = element_text(size=6)) +
  theme(axis.text.y = element_text(size=6)) +
  theme(axis.text.x = element_text(size=6)) +
  #guides(color = guide_legend(nrow = 2)) +
  theme(legend.key.size = unit(3, "mm"))

@@

# func <- function(t3)
# {
#   return(data.frame(COR = cor(t3$socialBlame, t3$perGini)))
# }
# df.cor <- ddply(t3, .(group1), func)
# t4 <- join(t3,df.cor,by="group1")
# cnames <- round(stats:::aggregate.formula(cbind(socialBlame, perGini) ~ COR, data=t4, mean),2)
plot1 <- ggplot(t4, aes(x=perGini, y=socialBlame, 
                        label=cntry)) +
  geom_smooth(method=lm, se=FALSE,  alpha=.5, linetype="dashed", size=0.5) +
  geom_text(size=2, vjust=-0.8, hjust=0.5) +
#   geom_text(data=cnames, aes(perGini,socialBlame, label = COR, group=COR), 
#             size=2.5, color="black") +
  labs(x = "Perceived inequality from data", 
       y = "Support for social blame type of explanation (%)") +
  geom_point(size=1.5) +
  geom_point(data=t4, aes(x=perGini, 
                          y=socialBlame, color=group_general)) +
  # west reference
  geom_point(data=west, aes(x=perGini, 
                            y=socialBlame, 
                            color=group_general), alpha=.5) +
  geom_text(data=west, aes(x=perGini, 
                           y=socialBlame, label=cntry),
             alpha=.5, size=2, vjust=-0.8, hjust=0.5) +
  # west reference
  scale_colour_manual(values=cbPalette) +
  #coord_cartesian(xlim=c(-2,2)) +
  theme_minimal() +
  theme(legend.title=element_blank()) +
  theme(legend.text=element_text(size=6)) +
  theme(legend.position="top") +
  theme(axis.title.y = element_text(size=6)) +
  theme(axis.title.x = element_text(size=6)) +
  theme(axis.text.y = element_text(size=6)) +
  theme(axis.text.x = element_text(size=6)) +
  #guides(color = guide_legend(nrow = 2)) +
  theme(legend.key.size = unit(3, "mm"))

# func <- function(t3)
# {
#   return(data.frame(COR = cor(t3$individualBlame, t3$perGini)))
# }
# df.cor <- ddply(t3, .(group1), func)
# t4 <- join(t3,df.cor,by="group1")
# cnames <- round(stats:::aggregate.formula(cbind(individualBlame, perGini) ~ COR, data=t4, mean),2)
plot2 <- ggplot(t4, aes(x=perGini, 
                        y=individualBlame, label=cntry)) +
geom_smooth(method=lm, se=FALSE,  alpha=.5, linetype="dashed", size=0.5) +
  geom_text(size=2, vjust=-0.8, hjust=0.5) +
#   geom_text(data=cnames, aes(perGini,individualBlame, label = COR, group=COR), 
#             size=2.5, color="black") +
  labs(x ="Perceived inequality from data", 
       y = "Support for individual blame type of explanation (%)") +
  geom_point(size=1.5) +
  geom_point(data=t4, aes(x=perGini, 
                          y=individualBlame, color=group_general)) +
  # west reference
  geom_point(data=west, aes(x=perGini, 
                            y=individualBlame, 
                            color=group_general), alpha=.5) +
  geom_text(data=west, aes(x=perGini, 
                           y=individualBlame, label=cntry),
             alpha=.5, size=2, vjust=-0.8, hjust=0.5) +
  # west reference
  scale_colour_manual(values=cbPalette) +
  #coord_cartesian(xlim=c(-2,2)) +
  theme_minimal() +
  theme(legend.title=element_blank()) +
  theme(legend.text=element_text(size=6)) +
  theme(legend.position="top") +
  theme(axis.title.y = element_text(size=6)) +
  theme(axis.title.x = element_text(size=6)) +
  theme(axis.text.y = element_text(size=6)) +
  theme(axis.text.x = element_text(size=6)) +
  #guides(color = guide_legend(nrow = 2)) +
  theme(legend.key.size = unit(3, "mm"))

@@

library(RColorBrewer)
library(mapproj)
library(maptools)
library(rgdal)
library(grid)
map <- suppressWarnings(readOGR(dsn="/home/aurelius/workspace/data/shapefiles/lits/", 
                                layer="lits_all_simple"))

### 2013-12-11 loadClean.Rmd
Tähän saakka tehtyä:
- koska gini-muuttujassa oli vähän ongelmia (1. tiedot vähän miltä vuosilta sattuu, 2. EI TILASTOLLISESTI MERKITSEVÄ, 3. teoreettisesti hieman epävarma) niin kokeilin laskea koetun eriarvoisuuden ginin aineistosta. Se on nyt mukana niin paperin kuvioissa kun myös ainakin osassa regressioita.
- Maaryhmittely on vielä mukana teksteissä, mutta sen voisi jättää kokonaan pois. Sitä ei ole analyyseissä ollutkaan hetkeen, mutta sen voisi jättää pois teoriasta, abstraktista ja todeta jotain siitä, miksi emme alaryhmittele post-sos maita.

Seuraavaksi:
- mun pitäisi kirjoittaa vähä

```{rLoadClean7, eval=TRUE}
#######
# Quality of governance
library(rustfare)
datQog <- GetQog(country = c('Armenia','Azerbaijan','Georgia','Russia',
                   'Ukraine','Moldova','Belarus','Kyrgyzstan',
                   'Kazakhstan','Tajikistan',
                   'Uzbekistan','Estonia','Latvia','Lithuania',
                   'Poland','Czech Republic','Slovakia','Hungary',
                   'Slovenia','Romania','Bulgaria',
                   'Italy','Germany','United Kingdom',
                   'Sweden','France'), 
       indicator = c("wbgi_vae"#, # World Bank - Voice and Accountability
                     #"uw_gini"
                     ))

@@

# subset the latest value per cntry per indicator
#library(plyr)
#datQogSum <- ddply(datQog, c("cname","indicator"), 
#                   subset, year == max(year))
datQogSum <- datQog[datQog$year %in% c(2006,2009),]
datQogSum$year[datQogSum$year == 2009] <- 2010
names(datQogSum)[3] <- "wbgi_vae"
datQogSum$indicator <- NULL

# datQogSum.w <- dcast(datQogSum, 
#                      cname+indicator ~ year, 
#                      value.var="value")

>>>>

```{rLoadClean7, eval=TRUE}
#######
# Quality of governance
library(rustfare)
datQog <- GetQog(country = c('Armenia','Azerbaijan','Georgia','Russia',
                   'Ukraine','Moldova','Belarus','Kyrgyzstan',
                   'Kazakhstan','Tajikistan',
                   'Uzbekistan','Estonia','Latvia','Lithuania',
                   'Poland','Czech Republic','Slovakia','Hungary',
                   'Slovenia','Romania','Bulgaria',
                   'Italy','Germany','United Kingdom',
                   'Sweden','France'), 
       indicator = c("wbgi_vae", # World Bank - Voice and Accountability
                     "uw_gini"
                     ))

@@

# subset the latest value per cntry per indicator
#library(plyr)
#datQogSum <- ddply(datQog, c("cname","indicator"), 
#                   subset, year == max(year))
datQogSum <- datQog[datQog$year %in% c(2006,2009),]
datQogSum$year[datQogSum$year == 2009] <- 2010
#names(datQogSum)[3] <- "wbgi_vae"
#datQogSum$indicator <- NULL

datQogSum.w <- dcast(datQogSum, 
                   cname+year ~ indicator, 
                       value.var="value")
